---
title: "R Project 1 - Hello R"
author: "Salvador Parada"
date: "Due Fed 3rd"
output: 
  html_document: 
    fig_width: 5
    highlight: espresso
    theme: cerulean
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

datasaurus_dozen file:  

How many rows? 1846  
How many columns? not found "help" data  
Variables included for the data frame? dataset, x, y  

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Correlation between 'x' and 'y' for star dataset:
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```

### Exercise 4

Circle dataset:

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Correlation between 'x' and 'y' for circle dataset:  

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))

```

### Exercise 5

Plot all datasets:  

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")

```

Generate summary correlation coefficients:  

```{r}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(13)
## `summarise()` ungrouping output (override with `.groups` argument)
## # A tibble: 13 x 2
##   dataset          r
##   <chr>        <dbl>
## 1 away       -0.0641
## 2 bullseye   -0.0686
## 3 circle     -0.0683
## 4 dino       -0.0645
## 5 dots       -0.0603
## 6 h_lines    -0.0617
## 7 high_lines -0.0685
## 8 slant_down -0.0690
## 9 slant_up   -0.0686
## 10 star      -0.0630
## 11 v_lines   -0.0694
## 12 wide_lines-0.0666
## 13 x_shape   -0.0656

```

